Interval Probability for Fuzzy Quantum Theories

### 2016-06-05 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} update comments...

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $P_{i}$, we have 
$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
\end{itemize}
\qed\end{definition}

@@

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. Since the non-additivity
operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$ is non-zero when
$S_{1}$ and $S_{2}$ does not commute.

>>>>

\begin{definition}[Quantum Probability
Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $P_{i}$, we have 
$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
\end{itemize}
\qed\end{definition}

@@

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. In the Dempster-Shafer
theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute.

A special feature of this theory is that it discusses the relation
between non-commuting subspaces while the real-valued quantum probability
measures in definition~\ref{def:QuantumProbabilitySpace} only depend
on orthogonal (or commuting) subspaces. Thinking a physical process
which put two non-commuting spaces together... Maybe two directions
of the first spin in the two-spin system?
